---
title: "IRM innovation tables preparation"
author: "A Farrow"
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include=FALSE}

options(width = 250, dplyr.width = 120)

#set (chunk) options - figure path is necessary to avoid an error message
knitr::opts_chunk$set(
  comment = NA,
  dpi = 96,
  echo = FALSE,
  #fig.path = paste0("figures/", params$INN1,"/"),
  warning = FALSE,
  cache = FALSE,
  include = TRUE
)

```

```{r libraries, echo=FALSE, message=FALSE, warning=FALSE, results='asis' }

library(tidyverse)
library(fuZR)
library(irm)
library(patchwork)
library(stringr)
library(ggplot2)
library(dplyr)
library(stringr)
library(readr)
library(tidyr)
library(kableExtra)
library(knitr)

```

# Check for existing requirements

## Load the innovations data frame

```{r existing_inn, echo=FALSE, message=FALSE, warning=FALSE, results='asis' }

df_inn <- read.csv("E:/repos/raise_fs/shiny/data/innovations.csv")
df_inn <- df_inn|> mutate(innovation = paste(crop_name, ideotype, scenario, sep = '-'))

df_inn |> kable(caption = paste("<h2 style=color:black;> Existing innovations</h2>")) |> kable_styling(
      bootstrap_options = "bordered",
      full_width = F,
      position = "left"
    ) |>  print()

```

## Define the biophysical innovation details:

```{r inn_choice_ba, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load transcribed biophysical data
crop_name_ba <- "barley"
crop_name_inn <- crop_name_ba
cat("\n### Crop =", crop_name_ba, "\n\n")

ideotype_ba <- "generic"
cat("\n### Ideotype =", ideotype_ba, "\n\n")

scenario_ba <- "generic"
cat("\n### Scenario =", scenario_ba, "\n\n")

combi_ba <- paste0(crop_name_ba,"-",ideotype_ba,"-", scenario_ba)
cat("\n### Biophysical requirements - Innovation =", combi_ba, "\n\n")

# If statement to check if combi_ba is in df_inn$innovation (case-insensitive)
if (any(grepl(combi_ba, df_inn$innovation, ignore.case = TRUE))) {
  cat("\n## BA - Match found!")
} else {
  cat("\n## BA - No match.")
}

```

## Define the socio-economic innovation details:

```{r inn_choice-sef, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# Load AHP socio-economic data

ideotype_sef <- "generic"
cat("\n### Ideotype =", ideotype_sef, "\n\n")

scenario_sef <- "generic"
cat("\n### Scenario =", scenario_sef, "\n\n")

combi_sef <- paste0(crop_name_inn,"-",ideotype_sef,"-", scenario_sef)
cat("\n### Socio-Economic requirements - Innovation =", combi_sef, "\n\n")


# If statement to check if combi_sef is in df_inn$innovation (case-insensitive)
if (any(grepl(combi_sef, df_inn$innovation, ignore.case = TRUE))) {
  cat("\n## SEF - Match found!")
} else {
  cat("\n## SEF - No match.")
}

```

## Combine details

```{r inn_compare, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# which is the most specific ideotype - ba or sef?


if (ideotype_ba == "generic" &
    ideotype_sef == "generic") {
  ideotype_inn  <-  "generic"
} else {if (ideotype_ba == "generic" &
         ideotype_sef != "generic") {
  ideotype_inn  <-  ideotype_sef
} else {if (ideotype_ba != "generic" &
         ideotype_sef == "generic") {
  ideotype  <-  ideotype_ba
} else {if (ideotype_ba != "generic" &
         ideotype_sef != "generic") {
  ideotype_inn  <-  ideotype_ba
  cat("MISMATCH")
  knit_exit(append, fully = TRUE)
}}}}

# which is the most specific scenario - ba or sef?

if (scenario_ba == "generic" &
    scenario_sef == "generic") {
  scenario_inn  <-  "generic"
} else {if (scenario_ba == "generic" &
         scenario_sef != "generic") {
  scenario_inn  <-  scenario_sef
} else {if (scenario_ba != "generic" &
         scenario_sef == "generic") {
  scenario_inn  <-  scenario_ba
} else {if (scenario_ba != "generic" &
         scenario_sef != "generic") {
  scenario_inn  <-  scenario_ba
  cat("MISMATCH")
  knit_exit(append, fully = TRUE)
}}}}

combi <- paste0(crop_name_inn,"-",ideotype_inn,"-", scenario_inn)

cat("\n### Requirements - Innovation =", combi, "\n\n")

# If statement to check if innovation is in df_inn$innovation (case-insensitive)
  if (any(grepl(combi, df_inn$innovation, ignore.case = TRUE))) {
    
     cat("\n ## Match found \n\n # EXITING!")
     
     keep_knit <- F
    
  } else {
    
    cat("\n ## No match.")
    keep_knit <- T
    
  }
```


```{r stop}

if (keep_knit == F) {
  
  knit_exit(fully = TRUE)
  
}
```


# Load existing data tables

## Requirements

Requirements data have already been transcribed from literature, and generated during calibration workshops.

It is possible that the biophysical requirements may be generic, while the socio-economic requirements may have been relevant for a specific ideotype or, more likely, a specific scenario.

In these cases the name of the whole innovation is that of the most specific of the two names.

```{r load_csv_ba, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df_ba <- read_csv(
  paste0(
    "E:/repos/raise_fs/tab_data/input/",
    crop_name_ba,
    "_",
    ideotype_ba,
    "_",
    scenario_ba,
    "_requirements.csv"
  ) ,
  locale = locale(encoding = "Latin1")
  
)

# remove rows with no data which have NA as crit_code

df_ba <- df_ba |> filter(!is.na(crit_code))


cat(
  "\ncsv file = E:/repos/raise_fs/tab_data/input/",
  crop_name_ba,
  "_",
  ideotype_ba,
  "_",
  scenario_ba,
  "_requirements.csv\n\n"
)

```


```{r load_csv_sef, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df_sef <- read_csv(
  paste0(
    "E:/repos/raise_fs/tab_data/input/AHP/AHP_",
    crop_name_inn,
    "_generic_generic_requirements.csv") , locale = locale(encoding = "Latin1")
  
)

# remove rows with no data which have NA as crit_code

df_sef <- df_sef |> filter(!is.na(crit_code))

cat("\ncsv file = E:/repos/raise_fs/tab_data/input/AHP/AHP_",
    crop_name_inn,
    "_generic_generic_requirements.csv\n\n")

```

## Weights

Weights are produced during the calibration workshop for socio-economic criteria.

No weights are produced during the transcription of biophysical requirements.


```{r load_csv_weights_ba, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df_weights_ba <- read_csv(
  paste0(
    "E:/repos/raise_fs/tab_data/input/",
    crop_name_ba,
    "_",
    ideotype_ba,
    "_",
    scenario_ba,
    "_weights.csv"
  ) ,
  locale = locale(encoding = "Latin1")
  
)

cat(
  "\ncsv weights file = E:/repos/raise_fs/tab_data/input/",
  crop_name_ba,
  "_",
  ideotype_ba,
  "_",
  scenario_ba,
  "_weights.csv\n\n"
)

```


Socio-economic criteria have a weights file and a higher-level rule bases file.

The weights file contains weights for both the lower-level and higher-level rule bases.

```{r load_csv_weights_sef, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df_weights_sef <- read_csv(
  paste0(
    "E:/repos/raise_fs/tab_data/input/AHP/AHP_",
    crop_name_inn,
    "_",
    ideotype_sef,
    "_",
    scenario_sef,
    "_weights.csv"
  ) ,
  locale = locale(encoding = "Latin1")
)

cat("\ncsv weights file = E:/repos/raise_fs/tab_data/input/AHP/AHP_",
    crop_name_inn,
    "_",
    ideotype_sef,
    "_",
    scenario_sef,
    "_weights.csv\n\n")

```


## Higher level rule bases


```{r load_csv_higher_sef, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df_higher_sef <- read_csv(
  paste0(
    "E:/repos/raise_fs/tab_data/input/AHP/AHP_",
    crop_name_inn,
    "_",
    ideotype_sef,
    "_",
    scenario_sef,
    "_higher.csv"
  ) ,
  locale = locale(encoding = "Latin1")
)

cat("\ncsv weights file = E:/repos/raise_fs/tab_data/input/AHP/AHP_",
    crop_name_inn,
    "_",
    ideotype_sef,
    "_",
    scenario_sef,
    "_higher.csv\n\n")

```

## Links between lower and higher level rule bases

```{r load_csv_links_sef, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df_links_sef <- read_csv(
  paste0(
    "E:/repos/raise_fs/tab_data/input/AHP/AHP_",
    crop_name_inn,
    "_",
    ideotype_sef,
    "_",
    scenario_sef,
    "_links.csv"
  ) ,
  locale = locale(encoding = "Latin1")
)

cat("\ncsv links file = E:/repos/raise_fs/tab_data/input/AHP/AHP_",
    crop_name_inn,
    "_",
    ideotype_sef,
    "_",
    scenario_sef,
    "_links.csv\n\n")

```

```{r load_csv_links_ba, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df_links_ba <- read_csv(
  paste0(
    "E:/repos/raise_fs/tab_data/input/",
    crop_name_ba,
    "_",
    ideotype_sef,
    "_",
    scenario_sef,
    "_links.csv"
  ) ,
  locale = locale(encoding = "Latin1")
)

cat("\ncsv links file = E:/repos/raise_fs/tab_data/input/",
    crop_name_inn,
    "_",
    ideotype_sef,
    "_",
    scenario_sef,
    "_links.csv\n\n")

```

# Merge existing data tables and ouput

## Requirements

```{r merge_df, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}


df_all_ba <- full_join(df_weights_ba, df_ba)

df_higher_weights_sef <- df_higher_sef |> full_join(df_weights_sef)

# Merge data frames and overwrite NA values in common variables
df_all_sef <-  left_join(df_higher_weights_sef, df_sef, by="crit_code") |> 
mutate(criterion= ifelse(is.na(criterion.y), criterion.x, criterion.y), conc_level_1 = ifelse(is.na(conc_level_1.y), conc_level_1.x, conc_level_1.y), conc_level_2 = ifelse(is.na(conc_level_2.y), conc_level_2.x, conc_level_2.y), conc_level_3 = ifelse(is.na(conc_level_3.y), conc_level_3.x, conc_level_3.y), .keep = "unused")

df_combined <- full_join(df_all_sef, df_all_ba) |> relocate(criterion, .after = crit_code) |> relocate(conc_level_1:conc_level_3, .after = prop_level_3)


df_combined |> kable(caption = paste("<h2 style=color:black;>", combi,"requirements merged</h2>")) |> kable_styling(
      bootstrap_options = "bordered",
      full_width = F,
      position = "left"
    ) |>  print()

```


```{r output_df, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# output the combined requirements table

  cat("\n ### No match.")
  
  write.csv(
    df_combined,
    paste0(
      "E:/repos/raise_fs/shiny/data/",
      crop_name_inn,
      "_",
      ideotype_inn,
      "_",
      scenario_inn,
      "_requirements.csv"
    ),
    row.names = FALSE
  )
  
  
  # add innovation to the table
  # automatic value for ID based on number of rows
  
  new_ID <- nrow(df_inn) + 1
  
  df_inn <- df_inn |> add_row(inn_ID = new_ID, crop_name = crop_name_inn,
                              ideotype = ideotype_inn,
                              scenario = scenario_inn) |> select(inn_ID, crop_name, ideotype, scenario) |> arrange(inn_ID, crop_name, ideotype, scenario)
  
  write.csv(df_inn, "E:/repos/raise_fs/shiny/data/innovations.csv", row.names = FALSE)


```

## Link between lower and higher levels

```{r merge_df_links, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}


df_links_combined <- full_join(df_links_sef, df_links_ba) |> left_join(select(df_combined, crit_code, weight), by = "crit_code")

df_links_combined |> kable(caption = paste("<h2 style=color:black;>", combi,"links merged</h2>")) |> kable_styling(
      bootstrap_options = "bordered",
      full_width = F,
      position = "left"
    ) |>  print()

```


```{r output_df_links, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# output the combined links table

  cat("\n ### No match.")
  
  write.csv(
    df_links_combined,
    paste0(
      "E:/repos/raise_fs/shiny/data/",
      crop_name_inn,
      "_",
      ideotype_inn,
      "_",
      scenario_inn,
      "_links.csv"
    ),
    row.names = FALSE
  )

```